GSS Education Analysis (Working Title)

### 2023-03-15 outputs/paper/paper.qmd
reorder paper and relabel graphs

#### Ordering ####

cleaned_gss_2021$degree <- 
  factor(cleaned_gss_2021$degree, 
         levels = c("Less Than High School", "High School", "Associate / Junior College", "Bachelors Degree", "Graduate Degree"))

@@

#### Ordering ####

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-4
#| fig-cap: "Respondent's Sex by Job Satisfaction"

#### Creating Graph to Compare Sex Against Job Satisfaction ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Job Satisfaction")+
  scale_fill_brewer(palette = "Pastel1")
```

@@

#### Ordering ####

```{r}
#| echo: false
#| warning: false
#| label: fig-5
#| fig-cap: "Respondent's Sex by Self-Defined Financial Ranking Against Other US Families"

#### Creating Graph to Compare Sex Against Self-Defined Financial Ranking Against Other US Families ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Rating Against Other Families")+
  scale_fill_brewer(palette = "Pastel1")
```

```{r}
#| echo: false
#| warning: false
#| label: fig-6
#| fig-cap: "Respondent's Highest Level of Education by Self-Defined Financial Ranking Against Other US Families"

#### Creating Graph to Compare Sex Against Self-Defined Financial Ranking Against Other US Families ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Rating Against Other Families")+
  scale_fill_brewer(palette = "Pastel1")+
  theme(legend.title = element_text(size = 6),
        legend.text= element_text(size=6))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-7
#| fig-cap: "Respondent's Highest Level of Education by Job Satisfaction"

#### Creating Graph to Compare Sex Against Job Satisfaction ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Job Satisfaction")+
  scale_fill_brewer(palette = "Pastel1")+
  theme(legend.title = element_text(size = 6),
        legend.text= element_text(size=6))
```

#### Ordering ####

```{r}
#| echo: false
#| warning: false
#| label: fig-15
#| fig-cap: "satfin vs degree"

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = satfin, fill = degree)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "satfin",
       x = "number",
       fill = "degree")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-17
#| fig-cap: "finrela vs satjob"

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = finrela, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "finrela",
       x = "number",
       fill = "satjob")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = finrela, fill = satfin)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "finrela",
       x = "number",
       fill = "satfin")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

>>>>

@@

#### Ordering Highest-Level of Education to be Easier to Read in Graphs####

cleaned_gss_2021$degree <- 
  factor(cleaned_gss_2021$degree, 
         levels = c("Less Than High School", "High School", "Associate / Junior College", "Bachelors Degree", "Graduate Degree"))
```

#### Ordering Job Satisfaction to be Easier to Read in Graphs####

@@

#### Ordering Self-Ascribed Financial Wellness Compared to Other US Families ####

#### Ordering Self-Ascribed Social Class of Respondents####

```{r}
#| echo: false
#| warning: false
#| label: fig-5
#| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Sex"

#### Creating Graph to Compare Respondent's Self-Ascribed Financial Ranking Against Other US Families by Sex ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number of Respondents",
       fill = "Rating Against Other US Families")+
  scale_fill_brewer(palette = "Pastel1")
```

```{r}
#| echo: false
#| warning: false
#| label: fig-6
#| fig-cap: "Respondent's Self-Asscribed Financial Ranking Against Other US Families by Their Highest Level of Education Achieved"

#### Creating Graph to Compare Respondent's Self-Asscribed FinancialRanking Against Other US Families by Their Highest Level of Education Achieved ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education Achieved",
       x = "Number of Respondents",
       fill = "Rating Against Other US Families")+
  scale_fill_brewer(palette = "Pastel1")+
  theme(legend.title = element_text(size = 6),
        legend.text= element_text(size=6))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-7
#| fig-cap: "Respondent's Report of Job Satisfaction by Their Highest Level of Education Achieved"

#### Creating Graph to Respondent's Report of Job Satisfaction by Their Highest Level of Education Achieved ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education Achieved",
       x = "Number of Respondents",
       fill = "Job Satisfaction")+
  scale_fill_brewer(palette = "Pastel1")+
  theme(legend.title = element_text(size = 6),
        legend.text= element_text(size=6))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-15
#| fig-cap: "Respondent's Report of Financial Satisfaction by Their Highest Level of Education Achieved"

#### Creating Graph to Compare Respondent's Report of Financial Satisfaction by Their Highest Level of Education Achieved ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = satfin, fill = degree)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Financial Satisfaction",
       x = "Number of Respondents",
       fill = "Highest Level of Education Achieved")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-17
#| fig-cap: "Respondent's Report of Job Satisfaction by Their Self-Asscribed Financial Ranking Against Other US Families"

#### Creating Graph to Compare Respondent's Report of Job Satisfaction by Their Self-Asscribed Financial Ranking Against Other US Families ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = finrela, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Rating Against Other US Families",
       x = "Number of Respondents",
       fill = "Job Satisfaction")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = finrela, fill = satfin)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Rating Against Other US Families",
       x = "Number of Respondents",
       fill = "Financial Satisfaction")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

@@
